Data Exploration: IUCN and AquaMaps

### 2015-11-30 R/data_explore_pt2.Rmd
still more ideas? new comparison of area vs overlap...

``` {r pct overlap vs area, echo = FALSE, warning = FALSE, message = FALSE}

@@

>>>>

``` {r pct overlap vs tot area, echo = FALSE, warning = FALSE, message = FALSE}

@@

``` {r pct overlap vs lg area, echo = FALSE, warning = FALSE, message = FALSE}

spp_list <- spp_list %>%
  mutate(lg_area = ifelse(am_area > iucn_area, am_area, iucn_area),
         sm_area = ifelse(am_area < iucn_area, am_area, iucn_area),
         lg_area_pct = 100 * lg_area / max(iucn_area, am_area, na.rm = TRUE)) ### use largest data set as approx for total ocean range

scatter_lg_area_vs_overlap <- ggplot(spp_list, aes(lg_area_pct, sm_perc, color = sm_range)) + 
  ggtheme_plot + 
  geom_point() + 
  geom_abline() + 
  labs(x = 'Larger range (% total ocean)', 
       y = 'Percent overlap smaller range in larger', 
       title = 'Percent overlap vs. larger range')

print(scatter_lg_area_vs_overlap)

ggsave(file.path(dir_fig, 'PercOverlapvsLgArea.png'), width = 6, height = 4)
